Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure - Supplementaty materials

### 2012-11-28 supplementary.tex
Added the TEM to the supplementary + a little bit to the reply

\section{TEM Imaging}
!!! It is quite obvious that it would be very interesting to aquire good TEM images of the nanoparticles  before and after a long oscillation measurement. However, due to the design of the $\mu$-reactor platform it is extremely difficult to get TEM images after reaction. This is partly due to the very thick substrate of seveal hundred $\mu$m, as well as the anodic bonding. The lid can only be removed by mechanically breaking the device. Figure ???? show a TEM image of a cluster ...... !!!

>>>>

\section{TEM Imaging}
!!! It is quite obvious that it would be very interesting to aquire good TEM images of the nanoparticles  before and after a long oscillation measurement. However, due to the design of the $\mu$-reactor platform it is extremely difficult to get TEM images after reaction. This is partly due to the very thick substrate of seveal hundred $\mu$m, as well as the anodic bonding, which cannot be reversed and thus the lid can only be removed by mechanically breaking the device. Images of the as-deposited particles are on the other hand quite easy to acquire by depositing on a substrate more suitable for TEM under conditions identical to those of the deposition into the $\mu$-reactor. Such an image is shown in Figure~\ref{fgr:gas_dependence}. Images of this kind confirms that our particles actually look like we expect them to do, but does not bring any insight into the oscillation mechanism or an explanation of the decrease in oscillation period as time progresses.!!!!
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{3nm_Pt_on_SiO2.png}
  \caption{Image of as-deposited nanoparticles deposited on a thin substrate of SiO$_2$.}
  \label{fgr:tem_3nm}
\end{figure}
